\begin{thebibliography}{1}

\bibitem{betterswing}
Better Swing, \emph{An easy way to develop java GUI apps}, V0.0.3. \hskip 1em plus
  0.5em minus 0.4em\relax Ver documentación completa \href{https://sergimayol.github.io/better-swing}{\textcolor{blue}{aquí}}.

\bibitem{Graphical engine}
Graphical engine, \emph{How to develop a graphical engine from scratch}. Ver enlace \href{https://www.youtube.com/watch?v=025QFeZfeyM&t=7334s}{\textcolor{blue}{aquí}}.

\bibitem{Gson}
Google json (Gson), \emph{Java serialization/deserialization library to convert Java Objects into JSON and back}. Ver enlace \href{https://github.com/google/gson}{\textcolor{blue}{aquí}}.

\bibitem{NodeJs architecture}
Node.js Architecture, \emph{Architecture of a single thread cross-platform, open-source server environment}. Ver enlace \href{https://codedamn.com/news/nodejs/node-js-architecture}{\textcolor{blue}{aquí}}.

\bibitem{Sqlite database}
The SQLite database, a serverless database. \emph{Quick start and documentation}. Ver enlace \href{https://www.sqlite.org/index.html}{\textcolor{blue}{aquí}}.

\bibitem{JFreeChart}
Open source Java chart library. \emph{An easy way to create and visualize charts in Java}. Ver enlace \href{https://www.jfree.org/jfreechart/}{\textcolor{blue}{aquí}}.

\bibitem{Method Overloading}
A way to define different behavior for a method with the same name. Ver enlace \href{https://www.geeksforgeeks.org/method-overloading-in-java/}{\textcolor{blue}{aquí}}.

\bibitem{RSA}
What is RSA? How does it work?. Ver enlace \href{https://es.wikipedia.org/wiki/RSA}{\textcolor{blue}{aquí}}.

\bibitem{Primality Test}
How to check if a number is prime. Ver enlace \href{https://en.wikipedia.org/wiki/Primality_test}{\textcolor{blue}{aquí}}.

\bibitem{Java BigInteger}
Java biginteger implementation and api docs reference. Ver enlace \href{https://docs.oracle.com/javase/8/docs/api/java/math/BigInteger.html}{\textcolor{blue}{aquí}}.

\bibitem{Pandas and Numpy}
Pandas and numpy for data analysis and visualization. Ver enlace Pandas: \href{https://pandas.pydata.org/}{\textcolor{blue}{aquí}}. Ver enlace Numpy: \href{https://numpy.org/}{\textcolor{blue}{aquí}} .

\bibitem{Jupyter Notebooks}
Jupyter notebooks for data analysis and visualization. Ver enlace \href{https://jupyter.org/}{\textcolor{blue}{aquí}}.

\bibitem{Trial division}
Trial division for integer factorization. Ver enlace \href{https://en.wikipedia.org/wiki/Trial_division}{\textcolor{blue}{aquí}}.

\bibitem{Fermat primality test}
Fermat primality test to determine whether a number is a probable prime. Ver enlace \href{https://en.wikipedia.org/wiki/Fermat_primality_test}{\textcolor{blue}{aquí}}.

\bibitem{Miller–Rabin primality test}
Miller–Rabin primality test to determine whether a number is a probable prime. Ver enlace \href{https://en.wikipedia.org/wiki/Miller%E2%80%93Rabin_primality_test}{\textcolor{blue}{aquí}}.

\bibitem{Thread pools in Java}
How to work with thread pools in Java. Ver enlace \href{https://www.baeldung.com/thread-pool-java-and-guava}{\textcolor{blue}{aquí}}.

\bibitem{Modular exponentiation}
Modular exponentiation. Ver enlace \href{https://en.wikipedia.org/wiki/Modular_exponentiation}{\textcolor{blue}{aquí}}.

\bibitem{Modular multiplicative inverse}
Modular multiplicative inverse. Ver enlace \href{https://en.wikipedia.org/wiki/Modular_multiplicative_inverse}{\textcolor{blue}{aquí}}.

\end{thebibliography}